Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-04-29 awipev-CO2.Rmd
RDM updated with new seaFET/durafet measurements 2/2

# set deployment period between 2 spectro measurements.
# add here the new periods durinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_dur = ifelse(datetime >= durinterv[1] & datetime <= durinterv[2], 01, 
                                ifelse(datetime >= durinterv[2] & datetime <= durinterv[3], 02, 
                                ifelse(datetime >= durinterv[3] & datetime <= durinterv[4], 03, 
                                ifelse(datetime >= durinterv[4] & datetime <= durinterv[5], 04,
                                ifelse(datetime >= durinterv[5] & datetime <= durinterv[6], 05,
                                ifelse(datetime >= durinterv[6] & datetime <= durinterv[7], 06,
                                ifelse(datetime >= durinterv[7] & datetime <= durinterv[8], 07,
                                ifelse(datetime >= durinterv[8] & datetime <= durinterv[9], 08,
                                ifelse(datetime >= durinterv[9] & datetime <= durinterv[10], 09,
                                ifelse(datetime >= durinterv[10] & datetime <= durinterv[11], 10, 
                                ifelse(datetime >= durinterv[11] & datetime <= durinterv[12], 10,
                                ifelse(datetime >= durinterv[12] & datetime <= durinterv[13], 10,NA )))))))))))))

@@

# create offset per period + add this offset per period.
d_all <- d_all%>%
 dplyr::mutate(offset_durafet = ifelse(deployment_dur == 1, dat_dur$diff_pH_dur[1],
                                ifelse(deployment_dur == 2, dat_dur$diff_pH_dur[2],
                                ifelse(deployment_dur == 3, dat_dur$diff_pH_dur[3],
                                ifelse(deployment_dur == 4, dat_dur$diff_pH_dur[4],
                                ifelse(deployment_dur == 5, dat_dur$diff_pH_dur[5],
                                ifelse(deployment_dur == 6, dat_dur$diff_pH_dur[6],
                                ifelse(deployment_dur == 7, dat_dur$diff_pH_dur[7],
                                ifelse(deployment_dur == 8, dat_dur$diff_pH_dur[8],
                                ifelse(deployment_dur == 9, dat_dur$diff_pH_dur[9],
                                ifelse(deployment_dur == 10, dat_dur$diff_pH_dur[10], 
                               ifelse(deployment_dur == 11, dat_dur$diff_pH_dur[11],
                                ifelse(deployment_dur == 12, dat_dur$diff_pH_dur[12],0)))))))))))),
              pH_durafet_corrected = pH_durafet + offset_durafet
              )
# DURAFET 
durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field,pH_durafet_corrected)
durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
 dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
    dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_durafet_corrected", label = "pH durafet corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2 ) %>%
    dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyShading(from =  durinterv[1], to= durinterv[2], color = "#CCCCCC") %>%
    dyShading(from = durinterv[2], to= durinterv[3], color = "#E0E0E0") %>%
    dyShading(from = durinterv[3], to= durinterv[4], color = "#CCCCCC") %>%
    dyShading(from = durinterv[4], to= durinterv[5], color = "#E0E0E0") %>%
    dyShading(from = durinterv[5], to= durinterv[6], color = "#CCCCCC") %>%
    dyShading(from = durinterv[6], to= durinterv[7], color = "#E0E0E0") %>%
   dyShading(from = durinterv[7], to= durinterv[8], color = "#CCCCCC") %>%
   dyShading(from = durinterv[8], to= durinterv[9], color = "#E0E0E0") %>%
   dyShading(from = durinterv[9], to= durinterv[10], color = "#CCCCCC") %>%
   dyShading(from = durinterv[10], to= durinterv[11], color = "#E0E0E0") %>%
    dyShading(from = durinterv[11], to= durinterv[12], color = "#CCCCCC") %>%
    dyShading(from = durinterv[12], to= durinterv[13], color = "#E0E0E0") %>%
   dyShading(from = durinterv[13], to= durinterv[14], color = "#CCCCCC") %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

>>>>

# set deployment period between 2 spectro measurements.
# add here the new periods durinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_dur = ifelse(datetime >= durinterv[1] & datetime <= durinterv[2], 01, 
                                ifelse(datetime >= durinterv[2] & datetime <= durinterv[3], 02, 
                                ifelse(datetime >= durinterv[3] & datetime <= durinterv[4], 03, 
                                ifelse(datetime >= durinterv[4] & datetime <= durinterv[5], 04,
                                ifelse(datetime >= durinterv[5] & datetime <= durinterv[6], 05,
                                ifelse(datetime >= durinterv[6] & datetime <= durinterv[7], 06,
                                ifelse(datetime >= durinterv[7] & datetime <= durinterv[8], 07,
                                ifelse(datetime >= durinterv[8] & datetime <= durinterv[9], 08,
                                ifelse(datetime >= durinterv[9] & datetime <= durinterv[10], 09,
                                ifelse(datetime >= durinterv[10] & datetime <= durinterv[11], 10, 
                                ifelse(datetime >= durinterv[11] & datetime <= durinterv[12], 11,
                                ifelse(datetime >= durinterv[12] & datetime <= durinterv[13], 12,
                                        ifelse(datetime >= durinterv[13] & datetime <= durinterv[14], 13,NA ))))))))))))))

@@

# create offset per period + add this offset per period.
d_all <- d_all%>%
 dplyr::mutate(offset_durafet = ifelse(deployment_dur == 1, dat_dur$diff_pH_dur[1],
                                ifelse(deployment_dur == 2, dat_dur$diff_pH_dur[2],
                                ifelse(deployment_dur == 3, dat_dur$diff_pH_dur[3],
                                ifelse(deployment_dur == 4, dat_dur$diff_pH_dur[4],
                                ifelse(deployment_dur == 5, dat_dur$diff_pH_dur[5],
                                ifelse(deployment_dur == 6, dat_dur$diff_pH_dur[6],
                                ifelse(deployment_dur == 7, dat_dur$diff_pH_dur[7],
                                ifelse(deployment_dur == 8, dat_dur$diff_pH_dur[8],
                                ifelse(deployment_dur == 9, dat_dur$diff_pH_dur[9],
                                ifelse(deployment_dur == 10, dat_dur$diff_pH_dur[10], 
                               ifelse(deployment_dur == 11, dat_dur$diff_pH_dur[11],
                                ifelse(deployment_dur == 12, dat_dur$diff_pH_dur[12],
                                       ifelse(deployment_dur == 13, dat_dur$diff_pH_dur[13],0))))))))))))),
              pH_durafet_corrected = pH_durafet + offset_durafet
              )
# DURAFET 
durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field,pH_durafet_corrected)
durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
 dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
    dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_durafet_corrected", label = "pH durafet corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2 ) %>%
    dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyShading(from =  durinterv[1], to= durinterv[2], color = "#CCCCCC") %>%
    dyShading(from = durinterv[2], to= durinterv[3], color = "#E0E0E0") %>%
    dyShading(from = durinterv[3], to= durinterv[4], color = "#CCCCCC") %>%
    dyShading(from = durinterv[4], to= durinterv[5], color = "#E0E0E0") %>%
    dyShading(from = durinterv[5], to= durinterv[6], color = "#CCCCCC") %>%
    dyShading(from = durinterv[6], to= durinterv[7], color = "#E0E0E0") %>%
   dyShading(from = durinterv[7], to= durinterv[8], color = "#CCCCCC") %>%
   dyShading(from = durinterv[8], to= durinterv[9], color = "#E0E0E0") %>%
   dyShading(from = durinterv[9], to= durinterv[10], color = "#CCCCCC") %>%
   dyShading(from = durinterv[10], to= durinterv[11], color = "#E0E0E0") %>%
    dyShading(from = durinterv[11], to= durinterv[12], color = "#CCCCCC") %>%
    dyShading(from = durinterv[12], to= durinterv[13], color = "#E0E0E0") %>%
   dyShading(from = durinterv[13], to= durinterv[14], color = "#CCCCCC") %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)
